full title

### 2020-11-17 paper/pldi21/eval.tex
First draft

@@

@@

\begin{table*}
  \centering
  \scriptsize
  \[
    \begin{array}{c|l|@{~}r@{~}c@{~}r@{~}r@{~}?c|l|@{~}r@{~}c@{~}r@{~}r@{~}?c|l|@{~}r@{~}c@{~}r@{~}r@{~}}
      \myhead
      \mysucc{2}{Boolean}   {Boolean}         {214}{214}{100} & \mydata{1}{}            {new Object}        {214}{214}{100} & \mymult{2}{Number}      {valueOf}       {214}{214}{100} \mylineff
      \mydata{1}{}          {new Boolean}     {214}{214}{100} & \mydata{1}{}            {getPrototypeOf}    {214}{214}{100} & \myname{1}{.prototype}                                  \mylinetft
      \mydata{1}{Array}     {isArray}         {214}{214}{100} & \mydata{1}{}            {create}            {214}{214}{100} & \mymult{2}{RegExp}      {toString}      {214}{214}{100} \mylinetf
      \mydata{1}{}          {toString}        {214}{214}{100} & \mydata{1}{Object}      {preventExtensions} {214}{214}{100} & \myname{1}{.prototype}                                  \mylinefft
      \mydata{1}{}          {toLocaleString}  {214}{214}{ 90} & \mydata{1}{}            {isFrozen}          {214}{214}{100} & \mydata{2}{String}      {String}        {214}{214}{100} \mylinefff
      \mydata{1}{}          {concat}          {214}{214}{100} & \mydata{1}{}            {isExtensible}      {214}{214}{100} & \mydata{1}{}            {fromCharCode}  {214}{214}{100} \mylinefft
      \mydata{1}{}          {join}            {214}{214}{100} & \mydata{1}{}            {keys}              {214}{214}{100} & \mydata{1}{}            {charAt}        {214}{214}{100} \mylineftf
      \mysucc{1}{Array}     {pop}             {214}{214}{100} & \mydata{1}{Object}      {valueOf}           {214}{214}{100} & \mydata{1}{}            {charCodeAt}    {214}{214}{100} \mylinefff
      \mydata{1}{.prototype}{push}            {214}{214}{100} & \mydata{1}{.prototype}  {isPrototypeOf}     {214}{214}{100} & \mydata{1}{}            {indexOf}       {214}{214}{100} \mylineftf
      \mydata{1}{}          {slice}           {214}{214}{100} & \mydata{1}{}            {acos}              {214}{214}{100} & \mysucc{1}{}            {match}         {214}{214}{100} \mylinefff
      \mydata{1}{}          {splice}          {214}{214}{100} & \mysucc{1}{}            {atan2}             {214}{214}{100} & \mydata{1}{String}      {replace}       {214}{214}{100} \mylinefff
      \mydata{1}{}          {map}             {214}{214}{100} & \mydata{1}{}            {cos}               {214}{214}{100} & \mydata{1}{.prototype}  {splice}        {214}{214}{100} \mylinefff
      \mydata{1}{}          {reduce}          {214}{214}{100} & \mydata{1}{Math}        {exp}               {214}{214}{100} & \mydata{1}{}            {split}         {214}{214}{100} \mylinetff
      \mysucc{1}{global}    {eval}            {214}{214}{100} & \mydata{1}{}            {floor}             {214}{214}{100} & \mysucc{1}{}            {substring}     {214}{214}{100} \mylinetff
      \mydata{1}{}          {new Date}        {214}{214}{100} & \mydata{1}{}            {max}               {214}{214}{100} & \mydata{1}{}            {toLowerCase}   {214}{214}{100} \mylinefff
      \mydata{1}{Date}      {parse}           {214}{214}{100} & \mydata{1}{}            {min}               {214}{214}{100} & \mydata{1}{}            {toUpperCase}   {214}{214}{100} \mylinef
      \mydata{1}{}          {now}             {214}{214}{100}
    \end{array}
  \]
  \caption{\todo}
  \label{fig:abs-analysis-ratio}
  \vspace*{-1.5em}
\end{table*}

\todo

>>>>

\begin{table*}
  \centering
  \caption{The number of \textit{abstracted} tests using dynamic shortcut
  instead of manual modeling for each JavaScript built-in library.}
  \label{table:func-replace}
  \vspace*{-1em}
  \scriptsize
  \[
    \begin{array}{c|l|@{~}r@{~}c@{~}r@{~}r@{~}?c|l|@{~}r@{~}c@{~}r@{~}r@{~}?c|l|@{~}r@{~}c@{~}r@{~}r@{~}}

      \myhead{Object}       {Function}        {\# Replaced}

      \mysucc{2}{Boolean}   {Boolean}         {214}{214}{100} & \mydata{1}{}            {new Object}        {214}{214}{100} & \mymult{2}{Number}      {valueOf}       {214}{214}{100} \mylineff
      \mydata{1}{}          {new Boolean}     {214}{214}{100} & \mydata{1}{}            {getPrototypeOf}    {214}{214}{100} & \myname{1}{.prototype}                                  \mylinetft
      \mydata{1}{Array}     {isArray}         {214}{214}{100} & \mydata{1}{}            {create}            {214}{214}{100} & \mymult{2}{RegExp}      {toString}      {214}{214}{100} \mylinetf
      \mydata{1}{}          {toString}        { 92}{139}{ 66} & \mydata{1}{Object}      {preventExtensions} {214}{214}{100} & \myname{1}{.prototype}                                  \mylinefft
      \mydata{1}{}          {toLocaleString}  {193}{214}{ 90} & \mydata{1}{}            {isFrozen}          {214}{214}{100} & \mydata{2}{String}      {String}        {214}{214}{100} \mylinefff
      \mydata{1}{}          {concat}          {214}{214}{100} & \mydata{1}{}            {isExtensible}      {214}{214}{100} & \mydata{1}{}            {fromCharCode}  {214}{214}{100} \mylinefft
      \mydata{1}{}          {join}            {214}{214}{100} & \mydata{1}{}            {keys}              {214}{214}{100} & \mydata{1}{}            {charAt}        {214}{214}{100} \mylineftf
      \mysucc{1}{Array}     {pop}             {214}{214}{100} & \mydata{1}{Object}      {valueOf}           {214}{214}{100} & \mydata{1}{}            {charCodeAt}    {214}{214}{100} \mylinefff
      \mydata{1}{.prototype}{push}            {214}{214}{100} & \mydata{1}{.prototype}  {isPrototypeOf}     {214}{214}{100} & \mydata{1}{}            {indexOf}       {214}{214}{100} \mylineftf
      \mydata{1}{}          {slice}           {214}{214}{100} & \mydata{1}{}            {acos}              {214}{214}{100} & \mysucc{1}{}            {match}         {214}{214}{100} \mylinefff
      \mydata{1}{}          {splice}          {214}{214}{100} & \mysucc{1}{}            {atan2}             {214}{214}{100} & \mydata{1}{String}      {replace}       {214}{214}{100} \mylinefff
      \mydata{1}{}          {map}             {214}{214}{100} & \mydata{1}{}            {cos}               {214}{214}{100} & \mydata{1}{.prototype}  {splice}        {214}{214}{100} \mylinefff
      \mydata{1}{}          {reduce}          {214}{214}{100} & \mydata{1}{Math}        {exp}               {214}{214}{100} & \mydata{1}{}            {split}         {214}{214}{100} \mylinetff
      \mysucc{1}{global}    {eval}            {214}{214}{100} & \mydata{1}{}            {floor}             {214}{214}{100} & \mysucc{1}{}            {substring}     {214}{214}{100} \mylinetff
      \mydata{1}{}          {new Date}        {214}{214}{100} & \mydata{1}{}            {max}               {214}{214}{100} & \mydata{1}{}            {toLowerCase}   {214}{214}{100} \mylinefff
      \mydata{1}{Date}      {parse}           {214}{214}{100} & \mydata{1}{}            {min}               {214}{214}{100} & \mydata{1}{}            {toUpperCase}   {214}{214}{100} \mylinef
      \mydata{1}{}          {now}             {214}{214}{100}
    \end{array}
  \]
  \vspace*{-1em}
\end{table*}

@@

\inred{TODO - Case Study.}

@@

The dynamic shortcut does not only improve performance or precision of analysis
but also reduce the effort to model the behavior of opaque functions.
JavaScript programs often use JavaScript built-in libraries or host-dependent
functions but they are opaque codes; it means that they are executable but
written in a different programming languages.  A typical solution is to
manually model their behaviors to statically analyze for JavaScript programs
using such functions.  The dynamic shortcut can reduce such efforts if some
opaque functions are analyzed by only dynamic analysis instead of static
analysis.

Table~\ref{table:func-replace} describes the dynamic shortcut effectively lessen
the burden of manual modeling for JavaScript built-in functions.  Among Lodash 4
\inred{219} abstracted tests analyzable with dynamic shortcut, we measured the
number of tests using only dynamic shortcut instead of manual modeling for each
JavaScript built-in library.  For each raw, \textbf{Object} column denotes the
built-in object, \textbf{Function} function name, \textbf{\# Replaced} the
number of tests successfully replacing the modeling via dynamic shortcut with
the total number of tests using the target function.  For example, the fourth
row in the left side describes that \jscode{Array.prototype.toString} is used in
\inred{139} Lodash 4 abstracted tests and the static analysis with dynamic
shortcut successfully analyze \inred{92} tests among them.  It means that
\inred{66}\% of tests using \jscode{Array.prototype.toString} could be analyzed
without the manual modeling of the built-in function.

Moreover, \inred{6} functions out of \inred{49} JavaScript built-in functions
are analyzed by only dynamic shortcut instead of manual modeling for all Lodash
4 tests.  Each raw colored colored with \inred{yellow} describes such case in
Table~\ref{table:func-replace}.  It means that the manual modeling of \inred{6} 
JavaScript built-in functions is does not required to analyze all Lodash 4
abstracted tests. \inred{TODO - Explain the detail for each case.}
